BurgerMax Presents: Open Adcess

### 2017-03-01 conclusion.tex
Draft pass

\section{Conclusion}
By bringing ACM up to date with the latest advertising techniques described in
this paper we believe that we can finally provide our papers to the masses for
free and at no cost to the authors.
Unfortunately, our trip to the future indicates that this idea works all too
well.
We release this knowledge onto the world knowing that the next generation must
pay for our free papers today with their work in the ACM dungeons and surrender
of their corporation.
We hope that future generations will somehow stop the beast that is the ACM
before it grows too powerful, but our own desire for fame outweighs our desire
to save our children from this madness.

>>>>

\section{Conclusion}
By bringing ACM up to date with the latest advertising techniques described in
this paper we believe that we can finally provide our papers to the masses for
free and at no cost to the authors.
Unfortunately, our trip to the future indicates that this idea works all too
well.
We release this knowledge onto the world knowing that the next generation must
pay for our free papers with their work in the ACM dungeons and surrender of
their corporations.
We hope that future generations will somehow stop the beast that is the ACM
before it grows too powerful, but our own desire for fame outweighs our desire
to save our children from this madness.

### 2017-03-01 digital-library.tex
Draft pass

\section{Digital Library}
\label{sec:lib}
Shady websites have long managed to monetize content downloads.
To provide free access to papers, we can follow their model by making the
following changes.

@@

By allowing advertisers to buy space on our digital library with which to
create ads that look like download buttons, advertisers can deceive users into
clicking an ad.
The advertiser and the ACM both profit off of these deceptive ads as the user
is redirected to see the advertiser's product while the ACM gets the revenue
for an impression. Some regulators have questioned this practice. But we believe it is a win-win-win for consumers \footnote{Gary Cohn, the director of the National Economic Council, stressed in an interview with *The Wall Street Journal* compared a website without fake-download buttons to the menu at P.J. Bland's: ``This is like putting only health food on the menu, because unhealthy food tastes good. But you still shouldn?t eat it because you might die younger." The menus of a free society, in his reckoning, should include both unhealthy and healthy items, and they should be labeled and priced identically. It should be impossible for consumers to access independent, third-party statistics about menu items. ``We believe our customers are informed and engaged, and we trust that they are smart enough to make the decisions that are right for them. We don't want the government treating them like dotards," the Gary Cohns said in unison.}.

@@

\subsection{ACM Digital Library Toolbar}
Like Java, every ACM paper will come as an executable.
Running this executable will ``install" the paper to the users desktop.
The only purpose of the install is to push the ACM Digital Library toolbar.
While the toolbar itself is optional, its installation is opt-out.
The ACM DL toolbar will be installed for all of the users web browsers where it
will follow them from site to site collecting information about their browsing
habits.
We will then sell this information to advertisers.

@@

>>>>

\section{Digital Library}
\label{sec:lib}
Shady websites have long managed to monetize free content downloads.
Below we detail the ways in which we can follow their example to provide free
access to papers.

@@

By allowing advertisers to buy space on our digital library with which to
create ads that look like download buttons, advertisers can deceive users into
clicking an ad.
The advertiser and the ACM both profit off of these deceptive ads as the user
is redirected to see the advertiser's product while the ACM gets the revenue
for an impression. Some regulators have questioned this practice. But we believe it is a win-win-win for consumers \footnote{Gary Cohn, the director of the National Economic Council, stressed in an interview with *The Wall Street Journal* compared a website without fake-download buttons to the menu at P.J. Bland's: ``This is like putting only health food on the menu, because unhealthy food tastes good. But you still shouldn't eat it because you might die younger." The menus of a free society, in his reckoning, should include both unhealthy and healthy items, and they should be labeled and priced identically. It should be impossible for consumers to access independent, third-party statistics about menu items. ``We believe our customers are informed and engaged, and we trust that they are smart enough to make the decisions that are right for them. We don't want the government treating them like dotards," the Gary Cohns said in unison.}.

@@

\subsection{ACM Digital Library Toolbar}
Every ACM paper will be distributed as an executable.
Running this executable will ``install" the paper to the users desktop.
The only purpose of the install is to push the ACM Digital Library toolbar on
the user.
While the toolbar itself is optional, its installation is opt-out.
The ACM DL toolbar will be installed for the user's web browsers where it
will follow them from site to site collecting information about their browsing
habits.
We will then sell this information to advertisers.

@@

In order to comply with New Jersey's backwards laws about involuntary Bitcoin
mining \cite{tidbit}, all New Jersey residents will be preemptively banned from
the ACM Digital Library.

### 2017-03-01 future-work.tex
Draft pass

\subsection{Introduction}
\paragraph{Introduction} An introduction is an explanatory section of a document that introduces the topic discussed in the document and presents a thesis statement.
\paragraph{Antithesis} Think about it, man. There is not introduction. We just see bad writing, cast as we are into this broken world.
\paragraph{Sublation} The introduction, some may argue

We think introductions leave those catching up with a field disoriented. More theater than truth, these sections do little to erase the veil of nonseeing from the student's mandatory raised unibrow, but -- please take a moment to recognize the taste of ACM Cola or the cool, refreshing ACM technology deity which (for all you just tuning in who forgot your mandatory religious training) we call Jerry -- the introduction

@@

As you may recall from \todo{sublation}, the engineers have ended the industrial dictatorship of the captains of finance as a matter of convenience

\subsection{Premium Edition}
To those who dislike the ads they see, ACM will offer a premium version for
2000 Linden dollars per year \footnote{In the future Linden dollars are the
one true world currency.
The value of 2000 L\$ in today's United States Dollar is currently unknown.}.
Unfortunately, due to high credit card processing fees we must still show ads
to premium edition subscribers.
However, these ads will be for more expensive products targeted towards those
with more ``refined" tastes.
We hope to solve this issue in the future with the creation of Bank of ACM.

\subsection{Ad-Free Edition}
For those who are physically able and enthusiastic about being part of
something big, the ACM offers ad free papers in exchange for manual labor at
your local ACM work dungeon.
This labor involves turning a very large crank around a pivot point in the
floor.
The crank is attached to a magnet spinning in a metal coil to generate the
necessary electricity required to power our servers.
However, all of this electricity is used to power electric lumbar support for
OSHA employees in exchange for their continued appreciation of the safe
practises within our work dungeons.
Two months of full time service provides access to five ad-free papers.
Professors may opt to have their graduate students turn the crank in their name
to count towards their service.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/mill.png}
  \caption{ACM work dungeon mill powered by 5th year grad student. Notice how our graduate students show great vigor and -- auscultate away! -- don't sound consumptive.}
  \label{fig:mill}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/horse-mill.jpg}
  \caption{12th year grad student sentenced to extra
  month in work dungeon for insufficient commitment to the mission of advancing
computing as a science and profession.
Not only is he a lifetime ACM member, but he's a lifehacker!  Shown here in his
ergonomic harness and standing desk.
OSHA would be proud.}
  \label{fig:horse-mill}
\end{figure}

@@

\subsection{Subvert Academic Thought}
Our native advertising proposal contained within the revolutionary Open Adcess
\cite{this} paper was much more effective than we ever could have imagined at
the time.
Rather than simply increasing brand awareness, we were able to transform
academic thinking away from mathematical and computational problems and
instead onto products and brands.
Computer scientists today have solved the worlds biggest problems in branding
and marketing while believing they were wasting all that brainpower on math.

\subsection{ACM Seizes Means of Production}
The ACM has successfully seized the means of production.
The mills that are now used to power our servers were previously used to grind
healing crystals into a fine powder.
This powder was slipped into the coffee of unsuspecting CEOs where it worked to
slowly make them more acceptable to the messages of the ACM.
After years of crystal ingestion, the CEOs of the world's largest companies
ceded control of their companies to the ACM.
We are happy to announce that there currently exist no companies other than the
ACM.

\subsection{Future Work}
A consequence of the invention of time travel \cite{time-travel} and the vanity
of engineers (not scientests) \cite{sci-shirt} is that people keep going
further back in time to give themselves credit for the invention of the time
machine.
However, we propose to go back in time for a different reason.
To put a stop to the Open Adcess.
To put a stop to the work dungeons.
And to put a stop to the ACM Revolution, which however noble in it's initial
goals has become  kinda lame.
We will open a mill based on anarchist principles that welcomes all to come and
mill and share healing crystals.
Our report of our screwing missadventuresduring our fieldtrip into the past can
be seen in the latest edition of \textit{Ubiquity} \cite{future-ub}.

>>>>

\subsection{Introduction}
\paragraph{Introduction} An introduction is an explanatory section of a document that introduces the topic discussed in the document and presents a thesis statement.
\paragraph{Antithesis} Think about it, man. There is no introduction. We just see bad writing, cast as we are into this broken world.
\iffalse
% Temporarily removed because I have no idea what this is
\paragraph{Sublation}
We think introductions leave those catching up with a field disoriented. More theater than truth, these sections do little to erase the veil of nonseeing from the student's mandatory raised unibrow, but -- please take a moment to recognize the taste of ACM Cola or the cool, refreshing ACM technology deity which (for all you just tuning in who forgot your mandatory religious training) we call Jerry -- the introduction

@@

As you may recall from \todo{sublation}, the engineers have ended the industrial dictatorship of the captains of finance as a matter of convenience
\fi

\subsection{Premium Edition}
To those who dislike the ads they see, ACM will offer a premium version for
2000 Linden dollars per year \footnote{In the future Linden dollars are the
one true world currency.
The value of 2000 L\$ in today's United States Dollar is not known.}.
Unfortunately, due to high credit card processing fees we must still show ads
to premium edition subscribers.
However, these ads will be for more expensive products targeted towards those
with more ``refined" tastes.
We hope to solve this issue in the future with the creation of The Bank of ACM.

\subsection{Ad-Free Edition}
For those who are physically able and enthusiastic about being part of
something big, the ACM offers ad free papers in exchange for manual labor at
your local ACM work dungeon.
This labor involves turning a very large crank around a pivot point in the
floor.
The crank is attached to a magnet spinning in a metal coil to generate the
necessary electricity required to power our servers.
However, all of this electricity is currently used to power electric lumbar
support for OSHA employees in exchange for their continued appreciation of the
safe practises within our work dungeons.
Two months of full time service provides access to five ad-free papers.
Professors may opt to have their graduate students turn the crank in their name
to count towards their service.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/mill.png}
  \caption{ACM work dungeon mill powered by 5th year grad student. Notice how
  our graduate students show great vigor!}
  \label{fig:mill}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/horse-mill.jpg}
  \caption{Lazy 12th year grad student sentenced to an extra
  month in the work dungeon for insufficient commitment to the mission of advancing
computing as a science and profession.
Not only is he a lifetime ACM member, but he's a lifehacker!  Shown here in his
ergonomic harness and standing desk.}
  \label{fig:horse-mill}
\end{figure}

@@

\subsection{Subvert Academic Thought}
Our native advertising proposal contained within the revolutionary Open Adcess
\cite{this} paper was much more effective than we ever could have imagined at
the time.
Rather than simply increasing brand awareness, we were able to transform
academic thinking away from mathematical and computational problems and
onto products and brands.
Computer scientists today have solved the worlds biggest problems in branding
and marketing while believing they were wasting all that brainpower on math.

\subsection{ACM Seizes Means of Production}
The ACM has successfully seized the means of production.
The mills that are now used to power our servers were previously used to grind
healing crystals into a fine powder.
This powder was slipped into the coffee of unsuspecting CEOs where it worked to
slowly make them more susceptible to the messages of the ACM.
After years of crystal ingestion, the CEOs of the world's largest companies
ceded control of their companies to the ACM.
We are happy to announce that there currently exist no companies other than the
ACM.

\subsection{Future Work}
A consequence of the invention of time travel \cite{time-travel} and the vanity
of engineers (not scientests) \cite{sci-shirt} is that people keep going
further back in time to give themselves credit for the invention of the time
machine.
However, we propose to go back in time for a different reason.
To put a stop to the Open Adcess.
To put a stop to the work dungeons.
And to put a stop to the ACM Revolution, which however noble in it's initial
goals has become  kinda lame.
We will open a mill based on anarchist principles that welcomes all to come and
mill and share healing crystals.
Our report of our screwing missadventures during our field trip into the past
can be seen in the latest edition of \textit{Ubiquity} \cite{future-ub}.

### 2017-03-01 paper-sponsorships.tex
Draft pass

\section{Paper Sponsorships}
\label{sec:sponsors}
In addition to ads on our Digital Library, we will also be adding
advertisements to the papers themselves.
These advertisements will come in many forms, including standard banner
advertisements as well as the increasingly popular native advertisement.

\subsection{Call for Advertisements}
Reach the largest holistic-minded audience in the entire northeastern United
States with an ad in the next ACM edition.
Our public mostly devoid of energy vampires and is therefore suitable for
empath advertisers.
Where IEEE uses Western proof verification techniques, our broad minded
audience validates mathematical claims in an intuitive holistic manner and will
bring that same spirit into evaluating the claims of your advertisements.
Our readers will engage with your brand through meditation and other
surprises.

\subsection{Banner ads}
Web surfers today have become accustom to seeing banner ads on their favorite
websites.
Therefore, we will be incorporating these advertisements into all of our
papers.
Advertisements can be easily inserted into existing \LaTeX\ papers through the
use of the \texttt{\textbackslash figure} and \texttt{\textbackslash figure*}
constructs.
Of course, advertisements using the two column \texttt{\textbackslash figure*}
width will be considerably more expensive than their one column brethren.
A standard 1 column ad can be seen in \autoref{fig:law} while a double-wide can
be found in \autoref{fig:usa}.

@@

\subsection{Ad Enhanced Fonts}
Computer Modern is a staple of modern papers, but we believe that this font can
be monetized.
By replacing the characters in the default latex with logos of companies we can
convey the same information in an ad enhanced way.

During each Call for Papers we will also put out a simultaneous Call for
Logos during which companies bid on which letter they want.
We require that the company logo is a stylized version of the letter being
replaced to avoid a Wingdings situation \cite{wingdings}.

@@

At paper registration time, authors will be given ad copy to integrate into
their work.
Each paper is required to have at least one section advertising the product
that was assigned to the research project.
As these ads are to be native, an advertisement that is recognizable as an ad
will result in a strong reject of the paper.
The ad section must be at least one page long, but there is no upper bound on
native ad length.
We recognize that this will eat into the page limits of some conferences so we
will allow authors to deduct the length of the native ad from their total paper
length provided that the length of the native section alone exceeds the total
page limit.
Authors can claim this deduction by filing a Form 8843 with their paper
submission.

\subsection{Branded mathematical objects}
\label{sec:brands}
We believe there has been a missed opportunity in the field of mathematics to
increase brand awareness.
Therefore, we propose branding mathematical objects by associating every single
set with an individual brand.
Brands can purchase large collections of sets at a discount.
While most sets are cheap, some more famous sets will sell for more to reflect
the higher market value, similar to domain names.
Thus, ACM will create an ICANN equivalent for these sets.

@@

We are excited to announce that our first partner in this endeavor will be
Chill's Grill \& Bar, who has purchased the rights to the set of natural
numbers.
From here on, authors must refer to this set as the Chill's Grill \& Bar Set of
Natural Numbers \(\mathbb{N}\)\copyright.

\subsection{Investor Author Dispute Settlement}
We have founded an Investor Author Dispute Settlement (IADS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle will dash the hopes of the typical Sparrow Soap
consumer they may use the IADS court to mitigate their losses from this
finding.
Moreover, since Sparrow Soap owns both of these complexity classes as defined
in section \autoref{sec:brands} their assets will lose value and
this loss must be compensated by the ``bloggers."

@@

\paragraph{Job Queue}
The Job Queue section contains odd jobs for trained Computer Scientists looking
for instant internet income.
Those who pay extra will get a free AirDancer\footnote{Placed at the discretion
of the ACM in the ACM AirDancer Oasis in the Black Rock Desert in Nevada in
solidarity with the aliens illegally detained in Area 51.  The AirDancers may
be used by the alien's to communicate with their home world}!
We will be posting the first jobs ourselves.

\paragraph{Overclock}
Overclock is a section for performance enhancing drugs tailored for computer
scientists.
This section is mostly targeted to the Hacker News \cite{hn} crowd who exclaims
the benefits of small amounts of LSD for enhancing productivity at work
\cite{microdose, lsd-song}.
Although we can't promote the use of illegal drugs our editor is so strung out
on ``road cheese" that she won't notice.
% http://www.forbes.com/sites/robertglatter/2015/11/27/lsd-microdosing-the-new-job-enhancer-in-silicon-valley-and-beyond/#323d0dab114d

>>>>

\section{Paper Sponsorships}
\label{sec:sponsors}
In addition to ads on our Digital Library, we will also be adding
advertisements to the papers themselves.
These advertisements will come in many forms, including standard banner
advertisements as well as increasingly popular native advertisements.

\subsection{Call for Advertisements}
Reach the largest holistic-minded audience in the entire northeastern United
States with an ad in the next ACM edition.
Our readership is mostly devoid of energy vampires and is therefore suitable
for empath advertisers.
Where IEEE uses Western proof verification techniques, our broad minded
audience validates mathematical claims in an intuitive holistic manner and will
bring that same spirit into evaluating the claims of your advertisements.
Our readers will engage with your brand through meditation and other
surprises.

\subsection{Banner ads}
Web surfers today have become accustom to seeing banner ads on their favorite
websites.
Therefore, we will be incorporating these advertisements into all of our
papers.
Advertisements can be easily inserted into existing \LaTeX\ papers through the
use of the \texttt{\textbackslash figure} and \texttt{\textbackslash figure*}
constructs.
Of course, advertisements using the two column \texttt{\textbackslash figure*}
construct will be considerably more expensive than their one column brethren.
A standard single column ad can be seen in \autoref{fig:law} while a
double-wide can be found in \autoref{fig:usa}.

@@

\subsection{Ad Enhanced Fonts}
Computer Modern is a staple of today's papers, but we believe that this font can
be monetized.
By replacing the characters in the default \LaTeX\ font with corporate logos
we can convey the same information in an ad enhanced way.

During each call for papers we will also put out a simultaneous call for
logos where companies can bid on desirable letters.
To avoid a Wingdings situation \cite{wingdings}, we require that the company
logo is a stylized version of the letter being replaced.

@@

At paper registration time, authors will be given ad copy to integrate into
their work.
Each paper is required to have at least one section advertising the product
that was assigned to the research project.
As these ads must be indistinguishable from the rest of the paper, an
advertisement that is recognizable as an ad will result in the rejection of the
paper.
The ad section must be at least one page long, but there is no upper bound on
native ad length.
We recognize that this will eat into the page limits of some conferences so we
will allow authors to deduct the length of the native ad from their total paper
length provided that the length of the native section alone exceeds the total
page limit.
Authors can claim this deduction by filing a Form 8843 with their paper
submission.

\subsection{Branded mathematical objects}
\label{sec:brands}
We believe there has been a missed opportunity in the field of mathematics to
increase brand awareness.
Therefore, we propose branding mathematical objects by associating every single
set with an individual brand.
Brands can purchase large collections of sets at a discount.
While most sets are cheap, some more famous sets will be priced higher to
reflect their higher market value, similar to domain names.

@@

We are excited to announce that our first partner in this endeavor will be
Chill's Grill \& Bar, who has purchased the rights to the set of natural
numbers.
From here on, authors must refer to this set as the Chill's Grill \& Bar Set of
Natural Numbers \(\mathbb{N}\).

\subsection{Investor Author Dispute Settlement}
We have founded an Investor Author Dispute Settlement (IADS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle, they will dash the hopes of the typical Sparrow Soap
consumer.
Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
this finding.
Moreover, since Sparrow Soap owns both of these complexity classes as defined
in section \autoref{sec:brands} their assets will lose value and
this loss must be compensated by the ``bloggers."

@@

\paragraph{Job Queue}
The Job Queue section contains odd jobs for trained Computer Scientists looking
for instant internet income.
Those who pay extra will get a free AirDancer\footnote{Placed at the discretion
of the ACM in the ACM AirDancer Oasis in the Black Rock Desert in Nevada in
solidarity with the aliens illegally detained in Area 51.  The AirDancers may
be used by the alien's to communicate with their home world.}!
We will be posting the first jobs ourselves.

\paragraph{Overclock}
Overclock is a section for performance enhancing drugs tailored for computer
scientists.
This section is mostly targeted at the Hacker News \cite{hn} crowd who exclaims
the benefits of small amounts of LSD for enhancing productivity at work
\cite{microdose, lsd-song}.
Although we can't promote the use of illegal drugs our editor is so strung out
on ``road cheese" that she won't notice.
% http://www.forbes.com/sites/robertglatter/2015/11/27/lsd-microdosing-the-new-job-enhancer-in-silicon-valley-and-beyond/#323d0dab114d
